### 2016-03-14 paper/algorithm.tex
yasu
minor changes

\section{Multi-way particle swarm fusion}
Multi-way Particle Swarm Fusion is a natural extension of the Fusion
Move method (FM). We call our method Swarm Fusion (SF) in short. Let us
take a multi-threading environment to explain our idea, while the
technique is also applicable to other parallel programming model such as
{\it MapReduce} in cloud computing.
%

Assuming we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$, each thread
$T_i$ maintains and updates a solution $S_i$ in parallel. Alpha
Expansion picks one label in each iteration to perform fusion. FM
generates a solution proposal via a proposal generation scheme.
%invokes one proposal generation scheme and generates a solution proposal
%for fusion.
SF has 1) a {\it proposal generator} which picks
arbitrary number of proposal generation schemes and generates proposals,
and 2) a {\it solution pool}, from which a thread picks arbitrary number
of intermediate solutions generated by the others.
% threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool remembers just the best
solution for each thread.

SF has two main parameters $\alpha_i$, $\beta_i$ (for each thread
$T_i$), determining its processing flow: In each fusion step, a thread
generates $\alpha_i$ solution proposals using its proposal generator, and collects
%\chen{A proposal pool sounds confusing. We often don't really maintain such a pool as many proposals are generated dynamically based on current solution. We just have certain strategies right there and in each iteration, we pick some strategies to generate proposals on the fly. This is different with the solution pool which is really there.}
$\beta_i$ solutions from the solution pool, based on a user-defined
strategy or at random to be simple. (The value of $\alpha_i$ and
$\beta_i$ can vary in each iteration to encourage different behaviors.)
The thread then fuse all these solutions together to find a solution
with lower energy state and update the solution pool accordingly.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.

Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
   Fusion (SF) architecture and its relationships to existing methods. The
 bottom right example shows the general SF architecture, where
 each thread takes arbitrary number of solution proposals and concurrent
 solutions from other threads for fusion. The framework is flexible and
 can realize other data processing architectures depending on the
 parameters (e.g., the left two examples in the bottom row).
 %
 % The left two examples at the
 % bottom row are other Swarm fusion architectures with some restrictions,
 % for which we provide comparative evaluations in
 % Section~\ref{section:results}.
 %
% The left two examples at the bottom are other Swarm fusion
% architectures with some restrictions, to be used for evaluations later.
 %
 It is easy to verify that existing popular MRF inference methods such
 as Alpha Expansion~\cite{alpha_expansion}, Fusion Move~\cite{fusion_moves_for_markov_random_field_optimization},
 Parallel Alpha Expansion~\cite{olga_hierarchical_alpha_expansion}, or Hierarchical
 Fusion~\cite{delong_hierarchical_fusion}, are all special cases of
 SF.}
\label{fig:model}
\end{figure}
%
The bottom right architecture is the most general one, in which threads
conduct multi-way fusion of solution proposals and/or concurrent
solutions (i.e., $\alpha\ne 0, \beta \ne 0$).
%
For general non-submodular energy, we use TRW-S~\cite{TRW-S, opengm} for inference.
%% And the energy is not submodular
%% in general, for which effective inference techniques such as
%% TRW-S~\cite{TRW-S,opengm} exist.
%
%, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
%compatible inference techniques can be used~\cite{opengm}.
However, if one knows that a certain fusion step is a binary fusion with
submodular energy, one can use
graph-cuts~\cite{alpha_expansion}. If a certain fusion step is a
binary fusion with non-submodular energy, one can use
QPBO~\cite{second_order_stereo}.
%
Note that the threads appear synchronized in the figure only for
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the solution pool (See
Algorithm~\ref{algorithm:sf}).
%The asynchronous computing further unleashes the power of parallism.
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  %\State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Generate $\alpha$ solution proposals $\mathcal{P}$ %\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  %\State [ Generates proposals and update $\mathcal{P}_{pool}$, if necessary ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

>>>>

\section{Multi-way particle swarm fusion} \label{section:algorithm}
Multi-way Particle Swarm Fusion is a natural extension of the Fusion
Move method (FM). We call our method Swarm Fusion (SF) in short. Let us
take a multi-threading environment to explain our idea, while the
technique is also applicable to other parallel programming model such as
{\it MapReduce} in cloud computing.
%

Assuming we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$,
each thread $T_i$ maintains and updates a solution $S_i$ in
parallel.
%Alpha
%Expansion picks one label in each iteration to perform fusion. FM
%generates a solution proposal via a proposal generation scheme.
%invokes one proposal generation scheme and generates a solution proposal
%for fusion.
SF has 1) a {\it proposal generator} which picks
arbitrary number of proposal generation schemes and generates proposals,
and 2) a {\it solution pool}, from which a thread picks arbitrary number
of intermediate solutions generated by the others.
% threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool remembers just the best
solution for each thread.

SF has two main parameters $\alpha_i$, $\beta_i$ (for each thread
$T_i$), determining its processing flow: In each fusion step, a thread
generates $\alpha_i$ solution proposals using its proposal generator, and collects
% \chen{A proposal pool sounds confusing. We often don't
% really maintain such a pool as many proposals are
% generated dynamically based on current solution. We just
% have certain strategies right there and in each iteration,
% we pick some strategies to generate proposals on the
% fly. This is different with the solution pool which is
% really there.}
$\beta_i$ solutions from the solution pool, based on a user-defined
strategy or at random to be simple. (The value of $\alpha_i$ and
$\beta_i$ can vary in each iteration to encourage different behaviors.)
The thread then fuse all these solutions together to find a solution
with lower energy state and update the solution pool accordingly.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.

Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
   Fusion (SF) architecture and its relationships to existing methods. The
 bottom right example shows the general SF architecture, where
 each thread takes arbitrary number of solution proposals and concurrent
 solutions from other threads for fusion. The framework is flexible and
 can realize other data processing architectures depending on the
 parameters (e.g., the left two examples in the bottom row).
 %
 % The left two examples at the
 % bottom row are other Swarm fusion architectures with some restrictions,
 % for which we provide comparative evaluations in
 % Section~\ref{section:results}.
 %
% The left two examples at the bottom are other Swarm fusion
% architectures with some restrictions, to be used for evaluations later.
 %
 It is easy to verify that existing popular MRF inference methods such
 as Alpha Expansion~\cite{alpha_expansion}, Fusion Move~\cite{fusion_moves_for_markov_random_field_optimization},
 Parallel Alpha Expansion~\cite{olga_hierarchical_alpha_expansion}, or Hierarchical
 Fusion~\cite{delong_hierarchical_fusion}, are all special cases of
 SF.}
\label{fig:model}
\end{figure}
%
The bottom right architecture is the most general one, in which threads
conduct multi-way fusion of solution proposals and/or concurrent
solutions (i.e., $\alpha\ne 0, \beta \ne 0$).
%
For general non-submodular energy, we use TRW-S~\cite{TRW-S, opengm} for inference.
%% And the energy is not submodular
%% in general, for which effective inference techniques such as
%% TRW-S~\cite{TRW-S,opengm} exist.
%
%, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
%compatible inference techniques can be used~\cite{opengm}.
However, if one knows that a certain fusion step is a binary fusion with
submodular energy, one can use
graph-cuts~\cite{alpha_expansion}. If a certain fusion step is a
binary fusion with non-submodular energy, one can use
QPBO~\cite{second_order_stereo}.
%
Note that the threads appear synchronized in the figure only for
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the solution pool (See
Algorithm~\ref{algorithm:sf}).
%The asynchronous computing further unleashes the power of parallism.
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  %\State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Generate $\alpha_i$ solution proposals $\mathcal{P}$ %\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta_i$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  %\State [ Generates proposals and update $\mathcal{P}_{pool}$, if necessary ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

### 2016-03-14 paper/optical_flow.tex

Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
solve the optical flow problem.
% Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and use images from the Middlebury optical
flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
generation schemes with Lempitsky et al~\cite{fusion_flow}, but
%instead of the HS algorithm, we
use more recent Farneback algorithm with some modifications.~\footnote{First, we
change the level of pyramids from 1 to 5, then use either 3, 5 or 7 for
parameter ``polyN''. Besides the clustering idea, we add three simple
proposal generation schemes based on the current solution as suggested
in \cite{fusion_flow}. In \textit{shift proposal}, the flow field in the
current solution is shifted in either x or y directions for
either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow field is
shifted by a vector randomly drawn from a Gaussian distribution. In
\textit{disturb proposal}, each flow value in the field is
indenpendantly shifted by a vector randomly drawn from a Gaussian
distribution. We choose schemes randomly when generating proposals.}

@@

\noindent Fusion Move method in Lempitsky's paper is the first natural
contender. While they did not consider parallel implementation, it is
straightforward to combine the idea of Parallel Alpha Expansion and
Fusion Move. Therefore, the second competing method is ``Parallel Fusion
Move''(PFM), which is equivalent to Parallel Alpha Expansion with constant
label solutions replaced by solution proposals.
%each thread repeats generating
%a solution proposal and fusing it to the current solution. Solutions
%from all the results are sequentially fused to obtain the final solution
%as in the Parallel Alpha-Expansion method.
%
One problem of PFM is that infinite number of solution proposals can be
generated in their algorithm, and we do not know when to stop and
perform the final sequential fusion (See Parallel Alpha Expansion
architecture in Fig.~\ref{fig:model}). In our experiments, we manually
picked time limits to initiate the final fusion to make the comparisons
fair.
%In Fig.~\ref{fig:model}, this computational framework corresponds to
%``parallel alpha-expansion'' with the label solutions replaced by
%solution proposals.
%
The last contender is the mix of the Hierarchical Fusion and the Fusion
Move methods, dubbed ``Hierarchical Fusion Method''(HFM), where they
start from solution proposals as opposed to constant labels. One problem
of HFM is that we need to generate all the proposals first to build the
fusion tree. This undermines the power of fusion move that can
adaptively generate proposals based on the current solution. In our
experiments, we have manually generate 250 proposals at the
beginning.
%We first generate 25 proposals using LK and Farneback algorithms which
%are independant and generate other proposals based on these initial
%proposals).
The fusions are binary in these methods and we have used QPBO.

\mysubsubsection{Swarm fusion architectures}

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
have been evaluated against the competing methods. For SF-MF, each
thread repeats generating solution proposals ($\alpha=1, \beta=0$) for 4
iterations and fuses with one solution from others ($\alpha=0, \beta=1$)
in one iteration. This pattern is repeated. For SF-SS, each thread
generates three solution proposals for fusion in each iteration
($\alpha=3$, $\beta=0$). For SF, we repeat ($\alpha=3, \beta=0$) for 4
iterations and ($\alpha=0, \beta=3$) for one iteration.
%%
%Note that we have used the same set of proposal generation schemes as
%the competing methods.
We have used TRW-S for multi-way fusion and QPBO for binary fusion.
% , while our fusions are multi-way, for which we have used TRW-S.
%
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
%
% 2 k-way 1 solution sharing. \chen{?}

>>>>

Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
solve the optical flow problem.
% Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and use images from the Middlebury optical
flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
generation schemes with Lempitsky et al~\cite{fusion_flow}, but
%instead of the HS algorithm, we
use more recent Farneback algorithm with some modifications.~\footnote{First, we
change the level of pyramids from 1 to 5, then use either 3, 5 or 7 for
parameter ``polyN''. Besides the clustering idea, we add three simple
proposal generation schemes based on the current solution as suggested
in \cite{fusion_flow}. In \textit{shift proposal}, the flow field in the
current solution is shifted in either x or y directions for
either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow field is
shifted by a vector randomly drawn from a Gaussian distribution. In
\textit{perturb proposal}, each flow value in the field is
independently shifted by a vector randomly drawn from a Gaussian
distribution. We choose schemes randomly when generating proposals.}

@@

\noindent Fusion Move method in Lempitsky's paper is the first natural
contender. While they did not consider parallel implementation, it is
straightforward to combine the idea of Parallel Alpha Expansion and
Fusion Move. Therefore, the second competing method is ``Parallel Fusion
Move''(PFM), which is equivalent to Parallel Alpha Expansion with constant
label solutions replaced by solution proposals.
%each thread repeats generating
%a solution proposal and fusing it to the current solution. Solutions
%from all the results are sequentially fused to obtain the final solution
%as in the Parallel Alpha-Expansion method.
%
One problem of PFM is that infinite number of solution proposals can be
generated in their algorithm, and we do not know when to stop and
perform the final sequential fusion (See Parallel Alpha Expansion
architecture in Fig.~\ref{fig:model}). In our experiments, we manually
picked time limits to initiate the final fusion to make the comparisons
fair.
%In Fig.~\ref{fig:model}, this computational framework corresponds to
%``parallel alpha-expansion'' with the label solutions replaced by
%solution proposals.
%
The last contender is the mix of the Hierarchical Fusion and the Fusion
Move methods, dubbed ``Hierarchical Fusion Move''(HFM), where they
start from solution proposals as opposed to constant labels. One problem
of HFM is that we need to generate all the proposals first to build the
fusion tree. This undermines the power of fusion move that can
adaptively generate proposals based on the current solution. In our
experiments, we have manually generate 250 proposals at the
beginning.
%We first generate 25 proposals using LK and Farneback algorithms which
%are independent and generate other proposals based on these initial
%proposals).
The fusions are binary in these methods and we have used QPBO.

\mysubsubsection{Swarm Fusion architectures}

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
have been evaluated against the competing methods. For SF-MF, each
thread repeats generating solution proposals ($\alpha=1, \beta=0$) for four
iterations and fuses with one solution from others ($\alpha=0, \beta=1$)
in one iteration. This pattern is repeated. For SF-SS, each thread
generates three solution proposals for fusion in each iteration
($\alpha=3$, $\beta=0$). For SF, we repeat ($\alpha=3, \beta=0$) for four
iterations and ($\alpha=0, \beta=3$) for one iteration.
%%
%Note that we have used the same set of proposal generation schemes as
%the competing methods.
We have used TRW-S for multi-way fusion and QPBO for binary fusion.
% , while our fusions are multi-way, for which we have used TRW-S.
%
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
%
% 2 k-way 1 solution sharing. \chen{?}

### 2016-03-14 paper/related_work.tex

MRF inference has been a very active field in Computer Vision with the
extensive literature. We refer the readers to survey articles for
comprehensive
reviews~\cite{middlebury_mrf,comparative_study_of_modern_inference}, and
here focus our description on closely related topics.

@@

\noindent Lempitsky et al. introduces parallel computation to an
alpha-expansion technique, where multiple threads simultaneously fuses
mutually exclusive sets of labels. Kumar et
al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
al.~\cite{delong_hierarchical_fusion}, and Veksler~\cite{olga_hierarchical_alpha_expansion} proposed an hierarchical
approach, where labels can be simultaneously fused from the bottom to
the top in a tree of labels. 
% 
Instead of taking a hierarchical approach, Batra et
al.~\cite{Dhruv_pushmeet_making_the_right_move} adaptively computed an
effective sequence of labels to explore. This technique can be combined
with parallel alpha-expansion techniques to further obtain speed-up.
%
Strictly speaking, these approaches are not in the family of Fusion Move
methods (FM), because they only consider constant label proposals. Our
approach is a generalization of FM.

@@

\noindent The core MAP inference itself can be parallelized.  Strandmark
et al. parallelized graph-cuts~\cite{strandmark_parallel}.
%
Message passing algorithms are friendly to GPU implementation and can
exploit the power of parallel computation.
%
%
While state-of-the-art optimization libraries are often freely available
for non-commercial purposes, most companies have to develop and maintain
in-house implementation of these algorithms.  The core optimization
libraries are very complex and their modifications require significant
engineering investments. In contrast, our idea is extremely simple and
easily reproducible by standard engineers.

@@

\mysubsubsection{Fusion Move Methods}

\noindent FM was first introduced by Lempitsky et al. in solving an
optical flow problem~\cite{fusion_flow}. FM has been effectively used to solve challenging
problems in Computer Vision such as stereo with second order smoothness
priors~\cite{second_order_stereo}, stereo with parameteric surface fitting and
segmentation (i.e., Surface Stereo)~\cite{surface_stereo}, or multicut
partitioning~\cite{fusion_moves_for_correlation_clustering}.
%
FM has two main advantages over the other general inference
techniques~\cite{TRW-S,loopy_belief_propagation}. First, FM allows us to
exploit domain-specific knowledge in customizing proposal generation
schemes. Second, FM can handle problems with very large label spaces
(and even real-values variables), because the core optimization
solves a sequence of binary decision problems.
%
In contrast, methods like message passing algorithms need to maintain
messages and beliefs for the entire label space all the time.
%
Although conceptually straightforward, we are not aware of {\it Parallel
Fusion move} algorithms that fuse solution proposals, as opposed to
labels, in parallel. This paper seeks to fully unleash the power of
parallel computation based on FM in the most general setting.
%for the most general FM via a more general framework.

@@

\noindent
Genetic algorithms (GA)~\cite{ga} and Particle Swarm
Optimization (PSO)~\cite{pso} maintain multiple solutions and improve
them over time.
%
GA or PSO has been used to produce great empirical results, for example,
hand tracking~\cite{pushmeet_hand_tracking}.
%
At high level, our strategy is similar in spirit. However, GA or PSO
rather arbitrarily copies parts of the solutions or makes random movements
in each step (i.e., limited theoretical justification).
%
Our approach directly optimizes the objective function to improve
solutions.

>>>>

MRF inference has been a very active field in Computer Vision with
extensive literature. We refer the readers to survey articles for
comprehensive
reviews~\cite{middlebury_mrf,comparative_study_of_modern_inference}, and
here focus our description on closely related topics.

@@

\noindent Lempitsky et al.~\cite{fusion_moves_for_markov_random_field_optimization} introduces parallel computation to an
alpha-expansion technique, where multiple threads simultaneously fuses
mutually exclusive sets of labels. Kumar et
al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
al.~\cite{delong_hierarchical_fusion}, and Veksler et al.~\cite{olga_hierarchical_alpha_expansion} proposed an hierarchical
approach, where labels can be simultaneously fused from the bottom to
the top in a tree of labels. 
% 
Instead of taking a hierarchical approach, Batra et
al.~\cite{Dhruv_pushmeet_making_the_right_move} adaptively computed an
effective sequence of labels to explore. This technique can be combined
with parallel alpha-expansion techniques to further obtain speed-up.
%
Strictly speaking, these approaches are not in the family of Fusion Move
methods (FM), because they only consider constant label proposals. Our
approach is a generalization of FM.

@@

\noindent The core MAP inference itself can be parallelized.  Strandmark
et al.~\cite{strandmark_parallel} parallelized graph-cuts.
%
Message passing algorithms are friendly to GPU implementation and can
exploit the power of parallel computation.
%
%
While state-of-the-art optimization libraries are often freely available
for non-commercial purposes, most companies have to develop and maintain
in-house implementation of these algorithms.  The core optimization
libraries are very complex and their modifications require significant
engineering investments. In contrast, our idea is extremely simple and
easily reproducible by standard engineers.

@@

\mysubsubsection{Fusion Move methods}

\noindent FM was first introduced by Lempitsky et al.~\cite{fusion_flow} in solving an
optical flow problem. FM has been effectively used to solve challenging
problems in Computer Vision such as stereo with second order smoothness
priors~\cite{second_order_stereo}, stereo with parameteric surface fitting and
segmentation (i.e. Surface Stereo)~\cite{surface_stereo}, or multicut
partitioning~\cite{fusion_moves_for_correlation_clustering}.
%
FM has two main advantages over the other general inference
techniques~\cite{TRW-S,loopy_belief_propagation}. First, FM allows us to
exploit domain-specific knowledge in customizing proposal generation
schemes. Second, FM can handle problems with very large label spaces
(and even real-values variables), because the core optimization
solves a sequence of binary decision problems.
%
In contrast, methods like message passing algorithms need to maintain
messages and beliefs for the entire label space all the time.
%
Although conceptually straightforward, we are not aware of {\it Parallel
  Fusion Move (PFM)} algorithms that fuse solution proposals, as opposed to
labels, in parallel. This paper seeks to fully unleash the power of
parallel computation based on FM in the most general setting.
% for the most general FM via a more general framework.

@@

\noindent
Genetic algorithms (GA)~\cite{ga} and Particle Swarm
Optimization (PSO)~\cite{pso} maintain multiple solutions and improve
them over time.
%
GA or PSO has been used to produce great empirical results,
hand tracking~\cite{pushmeet_hand_tracking} for example.
%
At high level, our strategy is similar in spirit. However, GA or PSO
rather arbitrarily copies parts of the solutions or makes random movements
in each step (i.e., limited theoretical justification).
%
Our approach directly optimizes the objective function to improve
solutions.
